### 2024-09-12 AISTAT25/aistats.tex
Removed hyphen in title
experimental section

\aistatstitle{Non-parametric active learning without smoothness}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3in]{figures/MassartExperiment.png}
\end{center}
\caption{{\bf Experimental evidence:} This figure compares the performance of passive sampling alone to that of the active learning algorithm. The X axis represents the number of queries made and the Y axis represents the difference between the error achieved and the optimal achievable error. }
\label{fig:Experiments}
\end{figure}

@@

We provide experimental evidence that our algorithm works. We chose a simple 1D problem, described in figure~\ref{}. Although this problem is simple, it is outside the scope of algorithms that assume that the conditional probability is smooth.

>>>>

\aistatstitle{Nonparametric active learning without smoothness}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3in]{figures/MassartExperiment.png}
\end{center}
\caption{{\bf Experimental evidence:} This figure compares the
  performance of passive sampling alone to that of the active learning
  algorithm. The X axis represents the number of queries made and the
  Y axis represents the difference between the error achieved and the
  optimal achievable error.}
\label{fig:Experiments}
\end{figure}

@@

We provide some experimental evidence that our algorithm is effective.
We chose a simple 1D problem, described in figure~\ref{fig:oned}(b)
(Massard Noise).  Although this problem is simple, it is outside the
scope of algorithms that assume that the conditional probability is a
smooth function of $x$. We used a sample of 2000 points and ran our
algorithm 10 times. In figure~\ref{fig:experiments} we present the
average error as a function of the number of queries. We compare the
performance of our active algorithm (red line) and the performance of the passive algorithm which is the
same algorithm where focused queries are disabled and only backgroud samples are used (blue line).

Observe that the error of the active algorithm decreases rapidly to
until iteration 600, while it takes 1,500 queries for the passive
algorithm to reach the same error. This almost three-fold improvement
demonstrates the effectiveness of our algorithm.
